TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-15 paper/draft.tex
crv caption

\begin{figure}[ht]
\plotone{figures/self_and_validation_test_teff_snr.png}
\plotone{figures/self_and_validation_test_feh_snr.png}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (left), and leave-one-out cross validation (right). Sources with strong rotational broadening (2M07171706−0501031, 2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles.} \label{fig:mann_validation}
\end{figure}

\begin{figure}[ht]
\begin{center}
\plotone{figures/self_and_validation_test_spt_snr.png}
\end{center}
\caption{Consistency test for the West-trained spectral type model; self-test (left), and leave-one-out cross validation (right).} \label{fig:west_validation}
\end{figure}

>>>>

\begin{figure}[ht]
\plotone{figures/self_and_validation_test_teff_snr.png}
\plotone{figures/self_and_validation_test_feh_snr.png}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (left), and leave-one-out cross validation (right). Sources with strong rotational broadening (2M07171706−0501031, 2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles. Predictive accuracy, as computed by the scatter in cross validation is 77K in temperature, and 0.09 dex in metallicity.} \label{fig:mann_validation}
\end{figure}

\begin{figure}[ht]
\begin{center}
\plotone{figures/self_and_validation_test_spt_snr.png}
\end{center}
\caption{Consistency test for the West-trained spectral type model; self-test (left), and leave-one-out cross validation (right).  Predictive accuracy, as computed by the scatter in cross validation is 0.9 subtypes.} \label{fig:west_validation}
\end{figure}
